SmartCheck: Automatic and Efficient Counterexample Reduction and Generalization

### 2012-12-30 paper/paper.tex
paper: more on precondition generalization.

@@

\todo{Add discussion here}

@@

\subsection{Automated Invariant Strengthening}

\todo{check all option names}

>>>>

\todo{make clear that preconditions shouldn't be considered logical preconditions}

@@

\todo{Add discussion here, note may be overapprox, since testing}

\subsection{Automated Precondition Strengthening}

The extrapolation algorithm generalizes a counterexample, but in the
``neighborhood'' of he original counterexample.  In particular, all
generalizations are from the same variant as the original counterexample.  To
help the programmer in the generalization step, we would also like a way to test
the property again, ensuring we get counterexamples (if they exist) outside of
the neighborhood of the original one.

Figure~\ref{fig:cex-gen} illustrates the situation in which we have some values
and a property in the case that some values fail the property of the form
(\ttp{pre ==> prop}).  Our goal is to find additional counterexamples in the
shaded region, in which \ttp{pre} is satisfied, \ttp{prop} is not satisfied, and
the counterexample is not already characterized by a universal sub-value
generalization formula.

\todo{talk about matches shape algorithm, real-eval-print}

@@
